\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }

\title{Entry 7-31-23}
\author{Long Nguyen}
\date{July 2023}

\begin{document}

\maketitle

\section{Paragraph}
I'm trying to write more essays now. Develop my ideas a little better. One obvious idea is that plants develop better with longer hours under grow lights. This is obvious, but also maybe not. The thing is that plants will die if the lights are never turned off. Plants need rest or sleep like humans do. It isn't exactly rest or sleep, but something analogous.whatever it is, just remember to turn off the lights for at least 6 hours, but other wise, keep them on.

\section{Rent control}
The final rent control vote in Seattle is coming up. I really hope it passes, but if it doesn't then it should show that the council members are not their to support their constituents the people. It should then demonstrate that people need to summon the political will to vote these monsters out of office. In any case, it's Shama's last year in office. After this, she'll be working with worker's strike back. I want to make a public comment in solidarity with everyone else who's going to be there. It feels like a contradiction though. This is because I'll be buying a house in Des Moines soon and I'm hoping to raise rents on the tenants there lol. This god damn system is aweful.

\section{Conservor society list}
What do I need to do to make a conserver society?
\begin{itemize}
	\item Rob Hopkin's transition towns
	\item Energy decent plan
	\item Permaculture
	\item Socialism
	\item Domocratic control of the state
	\item Social capital
	\item Lots of presentations
	\item Lots of speaking to people
\end{itemize}

\end{document}

