\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }

\title{talking to cops}
\author{Long Nguyen}
\date{March 2023}

\begin{document}

\maketitle

\section{Entry}
Once apon a time, houses were cheap. And now they are not. This is a story of an attempt to buy a duplex. There were complications and ups and downs and in the end, the it did not end. Now, how to start that story? Maybe in the beginning or the middle or the end. Best beginning in the beginning.
This duplex is suppose to be on sale for 499k and was negotiated down to 365k. This was done because the house was in major disrepair. An inspector was sent in and estimated the costs of fixing the house to be at least 100k. So it only seemed reasonable to negotiate that the owner either fix the issues or give a major discount. The discount price did not even nearly cover the potential cost of fixing the house.
So the cost came down to pretty much having to renovate the entire house. The worst things were the roof, the kitchen, the bathroom, and the water damage. There were minor damages and cosmetic adjustments needed everywhere as well.
The roof was at the end of its life and possibly causing the water damage. The bathroom was a biohazard. The inspector was surprised that it was even possible to shower given that the shower was leaking. He also found rust in the water. The bathroom was small in general, being even smaller because the water heater was right there inside the bathroom. The toilet was not secure, nor was the sink. It was certain that the entire bathroom would have to be redone. The kitchen was much better, but still many fixes were necessary. Doors were missing on cabinets and some burners were not working on the range. The sink was a mess, just because the rentors had not done the dishes. There was water damage found in the places previously mentioned, but also under the house. There could have been extensive damage, but that would only be found out if a plummer were called in.
Then there was all the minor issues that needed fixing. The entire outside of the house could be repainted. The yard was not maintained at all, so it needed to be weeded and watered regularly. The driveway was gravel and falling appart so it made driving up to the parking spot a hazard. Floors could be replaced. There was a mobile home next to the unit and that could not be fixed. The chimney was not maintained at all.
In all the house was a complete mess. Asking for 100k was warranted. As well as accepting just 50k was no large ask. It would be a complete wonder for this house to be sold at all. The seller may just come back and accept the offer being made. Now the next plan to go for a triplex or something in a higher price range, but that is move in ready and not in need to major fixes.

\end{document}

