\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }

\title{8/1/2023}
\author{Long Nguyen}
\date{August 2023}

\begin{document}

\maketitle

\section{Entry}
So what has happened today? First, I want to motivate this. It seems that people always have so much to say. I want to have a lot to say. In order for that, I need practice. I'll practice here. I'll try to make sure I have some stuff to say that is somewhat intelligible.

Now for the actual meat of the writing. I woke up and went to work. Nothing interesting happened. Mario did not let me do much. I might have made a crack in the reface, that Mario did not catch. Hopefully it is is not an issue. I left around 1pm and went to the Lynnwood transit center on the way to the Seattle city hall. The room was absolutely packed when I got there at 2:30. I had to watch from outside. The meeting in general was chaos because the council members wanted did not manage to schedule speakers correctly. They also limited the time for public speakers to one minute per speaker and only one total hour for all speakers. This meant that we could not get to the 80 in person speakers and 50 online speakers. At some point someone said "the popular opinion should not always be the political one" which is hiliarious considering that they would also say that we live in a democracy. In the end, the resolution was not passed. Shama ended the session with a little speech about learning from mistakes, about not trusting the democratic party, and how to move forward with workers strike back as a third party. Then I went to the U district with Gwen, Karl, and Olivia for food. Finally, I went to SA meeting.

\end{document}

