\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }

\title{talking to cops}
\author{Long Nguyen}
\date{March 2023}

\begin{document}

\maketitle

\section{Des Capital ch14 section 5}
An increase in laborers under one captialist is the sign of cooperation and manufacture. Division of labour makes an increase in labourers a necessity. Fixed capital being constant must be put back into the system, therefor captial must increase over time.

Manufacture creates hierarchic gradations. Co operation is benign while manufacture maimes the labourer by taking their creative juices and renders them into a cog in the machine. The detail work is distributed to individuals, this leaves the single worker as an automatic motor of a fractional operation. And now if the worker refuses work form the capitalist his function ceases to be useful as it was only necessary in the environment of the factory of the capitalist. Division of labor stamps the worker as the property of capital.

It starts off with co operation. Once the labourer sees its productiveness and starts to specialize, they are now under the control of capital in that end stage as a factory line worker. To make capital rich in social power, the labourer must be made poor in productiveness. Education of the masses violates the first law of division of labour argues a senator when Adam smith asserts that education would lift the vast majority of working poor of their poor lot. This is after Smith barages workers for their idiotness for these workers were born into detail labour and theirfore learn to fear stepping out of their bounds. 'The subdivision of labour is the assasination of people'. Co operation based on the division of labour is the definition of manufacture. The wealth of nations here Marx says refers to the division of labour profiting the capitalist at the expense of the labourer. It creates a power differential of capital over labour. It frames itself as a method of progress on one hand and on the other hand is a method of exploitation.

Political science was developed at the same time as period of manufacture. It only takes a view through manufacture as it is able to produce commodities. This means cheapening commodities in service of capital. Manufacture seperates labour into skilled and unskilled. Despite the seperation and then the seperation of class, the number of unskilled labourers remains very limited. Even with the exploitation of labourers who are women and children, the vices of capital are not sufficed to the satisfaction of the men doing the exploiting of labour. Even with seperation of work into detail work and into unskilled labour, some work still require apprenticeships that take a longer time to complete. These harder works are still desired even in spite of a lack of reward. Capital is constantly forced to wrestle with insubordination of workmen. 

\end{document}

