\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }

\title{SA bulletin #146}
\author{Long Nguyen}
\date{March 2023}

\begin{document}

\maketitle

\section{Exercise}
The idea of this exercise is to be able to first summerize a subject in one minute, then be able to expand on that topic for longer than a minute. For now, attempting 10 minutes is good enough. One day, it may be worth it to be able to lecture on a subject for days at a time. For this essay, one minute takes about 168 words. So for 10 minutes, 1680 words would be needed. This seems a little intense, so the goal will be a fourth of that at 420 words.

\section{Summary}
Socialist alternative has grown over the years. It must grow in order to become the radical marxian organization it aims to be. Its numbers in North America has rizen to 1000 starting from just 200 since 2010. This growth is due to the popularity of socialist ideas as well as the organizations ability to hold stead fast to socialist ideas. This also means that growth has to be controlled. Members initiation process can take months with many meetings, events, and dues. This is all to ensure the strength of the organiztion to hold steadfast to its core beliefs. And further growth of the organization is a must. A larger organization would allow for more influence in events such as the George Floyd protests. These events could be used as radicalizing events and as a means to push for further militarization. Of course the end goal is a socialist word where workers own the means of production and in which society is one that is stateless, moneyless, and classless.

\section{Dive}
In SA our organization is primarily made up of young people. We have 91 percent of our members being 35 years of age or younger. But we need to more specifically focus on the youth group. Due to Kshama relection campaign in 2019 and then covid in 2020, we could not do heavy campus drives. We need to retain ourselves in holding campus recruitment drives. This means tabling and holding topic discussions on campus. Thes topics most likely be on climate change, abortion rights, campus specific issues, and the far right push.

There is a chance to do a movie showing as the movie "The new corporation" is being released. This is a sequel to the movie "The corporation" which is a left leaning movie. This is a good change to partake in a fun activity that also raises some good questions as openings for chances at in depth discussions. We need to sell more papers to push our ideas out and inform people. Young people have always been at the forefront of struggle. This is why the youth is so important. Getting the youth would mean having a front line that is able to go out and fight for a better future. In addition to this, women must be included in the struggle. This is because they face ongoing and increasing oppression. This is because they are forced to take on many responsibilities as well as disadvantages. These include sexism, job discrimination, child care, elder care, housework, and through these pressures they could be key to linking comrads in the struggle.

Along with college students, high school students could also be recruited. We have had successful campaigns in highschools in the past were we have been able to discourage students from joining the military. Highschool students and young people are particularly acute to climate change and racial injustice. These are reasons why they resonate with soclialist alternative. Our material must stir up anger at the ruling class. We must come up with politics to combat climate change and move people to the left.

The protest after George Floyd shows the radicalizing power of being fed up with institutionalized racism. For this reason we have socialist alternative black caucus. The persuit of black justice is truly powerful. This is why we are coming up with a second edition of "Marxism and the fight for black freedom." NGOs, the democratic party, and left leaders all abducated responsiblity in the wake of the George Floyd protests. When given the power by the people in this key moment, our so called leaders chose to hide and do nothing with the all the energy available to them. DSA has shown their weakness as well in their black caucus. This is because their lean into identity politics had given them the wrong analysis. This analysis has lead to weak policies that do not move forward the black liberation cause. It is the role of the black liberation movement to spread that the key behind all opression is capitalism and it is the role of the class movement to combat racism.

\end{document}

