\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }

\title{}
\author{Long Nguyen}
\date{November 2023}

\begin{document}

\maketitle

\section{My Thoughts}
I don't like the way that I think. Almost every thought start with I, so that every thought is about myself.

This doesn't have to be the case. It's possible to think about the arab springs instead. It's possible to review what I had gone over in the day. What I had learned. Not about me, but specifically about the things that were not me.

I also have these thoughts pop up quite frequently. Like why don't I have enough money. This is usually when I think about some cringy thing in my past.

There is nothing wrong with thinking about myself. In fact, being self reflective could be a very good thing. The issue is being constantly reflexive and never looking at the outside world.

I have no issue looking into things other than myself when reading. Looking at media makes it much easier to look outwords. But in my head, the world revolves around me. I don't like that. I want to be able to have rich thoughts about other things when I am without media.

I want to be able to review topology. I want to be able to go over definition, examples, theorems. To maybe ask questions and explore the subject a way a mathemetician would.

I guess that's one good way to go about it as well. How do other people think? Did Einstein think about relativity and the photoelectric effect all day? How introspective was he? But I don't want to compare myself to Einstein, so lets think about Malia instead. What was floating around in her head? And how about Chi Ba? She's been helping David and me so much with the house. Does she think about herself in this whole thing? Does she think entirely about the house?

Then the obvious next question is what can I do? Well, I can recognize the problem. Whenever it comes up and I end up being too introspective, I can notice that and try to move onto something outword. The best idea would be to look at stuff I'm familiar with. Maybe look back into the past. Although, that would be a lot about me. Think about other people in the past. In my past, but other people. What were other people like? How did they react or talk? What did they like to do and what are they doing now? Be super curious about other people. Actually listen when people talk about themselves. Try constantly to reiterate what they have said in my own head.

Another subject I'm deeply intimate with is math, physics, and socialism. These are great topics to sharpen my thoughts on. Right now I'm going through Munkre's topology, so it would not be a bad idea at all to just think though the definitions, examples, and theorems. I can do the same for capital as well. There are not as many definitions, but Marx goes through a bunch of theory. He also talks about historical examples, It was current events to him. 

It is difficult to look outwords though. It always feels like I run out of thoughts when trying to do these things. Except when I rant about how aweful capitalism is. That usually takes me away from myself for a good couple minutes. 

I want to be able to have these 5-10 minute solilique though. It would also be awesome to be able to rant out loud to other people for about things not my life. It would be great to be a person of ideas. Someone you could go to and just listen to them lecture about something they are passionate about for hours on end.

I want that. I want hours worth of material not about myself that I can lecture people about. I don't necessarily want to lecture people for hours on end all the time. 

Possibly a good way to approach this is to write essays. That is not enough though. I would have to do a lot more with the essays. I have been writing essays. I wrote and entire leadoff on degrowth. This did not lead to the desired outcome that I wrote on above. To get that desire outcome would require a lot of hard work to review.

This probably means I have to be able to dig deeply into a subject matter. I might have to devote months into a certain subject. To the point where I cannot stop thinking about it. Then when the thoughts don't stop, I would have to let it out. And when I let it out, I want to be able to say that I could talk about it all day and actually be able to talk about it all day.

\end{document}

